Supplementary Material: District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-14 paper/supp_figs.tex

\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{todonotes}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{array}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{tikz}
\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{multirow}
\setlength{\tabcolsep}{5pt}
%%\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\renewcommand{\arraystretch}{1.5}

@@

@@

The study consisted of 33 sub-Saharan countries, which in approximate order from North to South and then West to East are: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Demorcratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa". 
We excluded 4 countries: Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana. These were excluded because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on circumcision.

We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \textbf{[Citations]}. 
Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
\textbf{[Expand on reasons for exclusions]} [Link in your survey figure] Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.

\begin{figure}[H]
    \centering
    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
    \caption{Household surveys detailing circumcision patterns in SSA. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type.}
    \label{fig:enter-label}
\end{figure}

@@

% \begin{landscape}
{\linespread{1}
\small
\begin{longtable}[c]{ll ccc ccc ccc ccc}
      %%%%%%%%%%%%%%%%%%%%
      %%% Table header %%%
      %%%%%%%%%%%%%%%%%%%%
      % Upper layer of table header
      \hline
      % Lines inside the header
      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
      \cmidrule(lr){5-7}
       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
      % Lower lines
      \hline
      \vspace{-5pt}
      \endhead
      %%%%%%%%%%%%%%%%%%%%
      %%% Table footer %%%
      %%%%%%%%%%%%%%%%%%%%
      \\[-5pt]\hline
      \caption{Table caption}
      \endfoot
      %%%%%%%%%%%%%%%%%%%%%%
      %%% Table contents %%%
      %%%%%%%%%%%%%%%%%%%%%%
      \multicolumn{2}{l}{\textbf{Angola}} \\
      & 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt]
      \multicolumn{2}{l}{\textbf{Burundi}} \\
      & 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
      & 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt]
      \multicolumn{2}{l}{\textbf{South Africa}} \\
      & 2002 (HSRC) &  \\
      & 2008 (HSRC) &  \\
      & 2012 (HSRC) &  \\
      & 2016 (DHS)  &  \\
      & 2017 (HSRC) &  
\end{longtable}
}
% \end{landscape}

>>>>

\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{todonotes}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{array}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{tikz}
\usepackage{pifont}
\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{multirow}
\setlength{\tabcolsep}{5pt}
%%\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\renewcommand{\arraystretch}{1.5}

@@

\newcommand{\xmark}{\ding{55}}

@@

The study consisted of 33 sub-Saharan countries, which in approximate order from North to South and then West to East are: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa". 
We excluded 4 SSA countries: Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana. These were excluded because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.

We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \textbf{[Citations]}. 
Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
\textbf{[Expand on reasons for exclusions]} \textbf{[Link in your survey figure]} 
Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework. The surveys which were excluded on the basis of this requirement were the Botswana 2008 BAIS and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys.
For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys. Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.
See table 1 for the full list of surveys for each country, and the circumcision information included in each survey.

\begin{figure}[H]
    \centering
    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.png}
    \caption{Household surveys detailing circumcision patterns in sub-Saharan Africa. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type.}
    \label{fig:enter-label}
\end{figure}

@@

% \begin{landscape}
{\linespread{1}
\small
\begin{longtable}[c]{ll ccc ccc ccc ccc}
      %%%%%%%%%%%%%%%%%%%%
      %%% Table header %%%
      %%%%%%%%%%%%%%%%%%%%
      % Upper layer of table header
      \hline
      % Lines inside the header
      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
      \cmidrule(lr){5-7}
       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
      % Lower lines
      \hline
      \vspace{-5pt}
      \endhead
      %%%%%%%%%%%%%%%%%%%%
      %%% Table footer %%%
      %%%%%%%%%%%%%%%%%%%%
      \\[-5pt]\hline
      \caption{Table caption}
      \endfoot

      %%%%%%%%%%%%%%%%%%%%%%
      %%% Table contents %%%
      %%%%%%%%%%%%%%%%%%%%%%
      \multicolumn{2}{l}{\textbf{Angola}} \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Benin}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Botswana}} \\ 
& 2008 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\ 
& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Burkina Faso}} \\ 
& 2003 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Burundi}} \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Cameroon}} \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Central African Republic}} \\ 
& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Chad}} \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Congo - Kinshasa}} \\ 
& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Côte d’Ivoire}} \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Eswatini}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \checkmark & \xmark \\ 
& 2010 (MICS) & \checkmark & \checkmark & \xmark & \xmark \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Ethiopia}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Gabon}} \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Gambia}} \\ 
& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Ghana}} \\ 
& 2003 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Guinea}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Guinea-Bissau}} \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Kenya}} \\ 
& 2003 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Lesotho}} \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2009 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
& 2014 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Liberia}} \\ 
& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Malawi}} \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2013 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Mali}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Mozambique}} \\ 
& 2003 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2009 (AIS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Namibia}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \checkmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Niger}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Nigeria}} \\ 
& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Repulic of the Congo}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2009 (AIS) & \checkmark & \xmark & \checkmark & \xmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Rwanda}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2008 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Senegal}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Sierra Leone}} \\ 
& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{South Africa}} \\ 
& 2002 (HSRC) & \checkmark & \checkmark & \xmark & \checkmark \\ 
& 2008 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2012 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2017 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Tanzania}} \\ 
& 2003 (AIS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2007 (AIS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2012 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Togo}} \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Uganda}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2011 (AIS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Zambia}} \\ 
& 2007 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
\multicolumn{2}{l}{\textbf{Zimbabwe}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt]

\end{longtable}
}
